---
title: "Bootstrap"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)
library(p8105.datasets)

set.seed(1)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Examples

### Bootstrapping in SLR
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

```

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```

```{r}
lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Drawing one bootstrap sample

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

500 times okay
more times are better(time-consuming)
random forest

```{r}
boot_straps = data_frame(
  strap_number = 1:1000,
  strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
)

boot_straps
```

some data are oversampled
others are underrepresented

every resample are different

```{r}
boot_straps %>% 
  filter(strap_number %in% 1:2) %>% 
  mutate(strap_sample = map(strap_sample, ~arrange(.x, x))) %>% 
  pull(strap_sample)
```

```{r}
boot_straps %>% 
  filter(strap_number %in% 1:3) %>% 
  unnest() %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_grid(~strap_number) 
```

Analyzing bootstrap samples

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(models = map(strap_sample, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest() %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))

bootstrap_results %>% 
  knitr::kable(digits = 3)
```
Correct standard error
intercept smaller
slope larger


```{r}
boot_straps %>% 
  unnest() %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)

boot_straps$strap[[1]]
 
as_data_frame(boot_straps$strap[[1]])
```

```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest() %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

the dataset with constant error variance

```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest() %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

### Non-standard parameters
works well with small sample size
```{r}
sim_df = 
  tibble(
    x = rnorm(25, 1, 1),
    error = rnorm(25, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest() %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

skewed--r^2 max=1---use 95% CI

```{r}
sim_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest() %>% 
  select(id = `.id`, term, estimate) %>% 
  spread(key = term, value = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = x) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

use quantile---quantile(log_b0b1, c(0.025, 0.975))

### Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest() %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```

